Research log

### 2024-01-10 docs/ExploratoryResults.Rmd
fixed error in analysis

@@

Next, we asked whether pretend games were not only more similar among themselves, but also to the average non-pretend game, than were non-pretend games. We therefore replaced the $\mu_{pretend}$ in the standard deviation formula with $\mu_{non-pretend}$: $\sigma'=\sqrt{\frac{1}{N}\Sigma_{i=1}^{N} (x_{i}-\mu_{non-pretend})^2}$. Strikingly, we find that a typical pretend game was more similar, in number of misses, **to the average non-pretend game**, than was a typical non-pretend game (`r apa_print(E2.sd_num_clicks_relative_to_np$diff%>%t.test())$full_result`).

@@

@@

In order to test whether pretend games were more similar to the average non-pretend game than non-pretend games themselves, we first regressed out the effect of word on number of misses, since within-subject differences between the conditions can reflect the random assignment of words to conditions. We then replaced the $\mu_{pretend}$ in the standard deviation formula with $\mu_{non-pretend}$: $\sigma'=\sqrt{\frac{1}{N}\Sigma_{i=1}^{N} (x_{i}-\mu_{non-pretend})^2}$, as we did for Battleship. We again find that a typical pretend game was more similar, in number of misses (controlling for word difficulty), to the average pretend game, than was a typical non-pretend game (`r apa_print(E4.sd_num_misses_relative_to_np_controlling_for_word_difficulty$diff%>%t.test())$full_result`).

@@

>>>>

p<- E2.click_df %>%
  filter(!(subj_id %in% E2.lucky_pretenders))%>%
  group_by(subj_id,test_part, genuine_first) %>%
  summarise(sd_num_clicks=sd(num_clicks)) %>%
  group_by(test_part)%>%
  summarise(
    mean=mean(sd_num_clicks),
    se=se(sd_num_clicks)
    ) %>%
  ggplot(aes(x=test_part,
             color=test_part,
             y=mean))+
  geom_point(size=10)+
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se),color='black')+
  scale_color_manual(values=c("#69b3a2", "#404080")) +

@@

<!-- Next, we asked whether pretend games were not only more similar among themselves, but also to the average non-pretend game, than were non-pretend games. We therefore replaced the $\mu_{pretend}$ in the standard deviation formula with $\mu_{non-pretend}$: $\sigma'=\sqrt{\frac{1}{N}\Sigma_{i=1}^{N} (x_{i}-\mu_{non-pretend})^2}$. Here, a typical pretend game was less similar, in number of misses, to the average non-pretend game, than was a typical non-pretend game (`r apa_print(E2.sd_num_clicks_relative_to_np$diff%>%t.test())$full_result`). -->

@@

p<- E2.click_entropy_by_serial_position_summary %>%
    filter(test_part %in% c('pretend','nonpretend') & click_number<=8) %>%
    ggplot(aes(x=click_number,y=mean_entropy,color=test_part,group=test_part)) +
    geom_line() +
    geom_ribbon(aes(ymax=mean_entropy+se_entropy,ymin=mean_entropy-se_entropy, fill=test_part),alpha=0.5) +
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725", "black")) +
    scale_color_manual(values=c("#69b3a2", "#404080", "black", "black")) +
    labs(x='click number', y='') +
    theme_classic() +
    scale_x_continuous(breaks=seq(20))+
  theme(legend.pos='na')

ggsave('figures/Battleship2/sequential_guess_entropy.png',width=2.5,height=1.5,dpi=300)

@@

<!-- In order to test whether pretend games were more similar to the average non-pretend game than non-pretend games themselves, we first regressed out the effect of word on number of misses, since within-subject differences between the conditions can reflect the random assignment of words to conditions. We then replaced the $\mu_{pretend}$ in the standard deviation formula with $\mu_{non-pretend}$: $\sigma'=\sqrt{\frac{1}{N}\Sigma_{i=1}^{N} (x_{i}-\mu_{non-pretend})^2}$, as we did for Battleship. We again find that a typical pretend game was less similar, in number of misses (controlling for word difficulty), to the average non-pretend game, than was a typical non-pretend game (`r apa_print(E4.sd_num_misses_relative_to_np_controlling_for_word_difficulty$diff%>%t.test())$full_result`).  -->

@@

p<- E4.click_entropy_by_serial_position_summary %>%
    filter(test_part %in% c('pretend','nonpretend') & click_number<=8) %>%
    ggplot(aes(x=click_number,y=mean_entropy,color=test_part,group=test_part)) +
    geom_line() +
    geom_ribbon(aes(ymax=mean_entropy+se_entropy,ymin=mean_entropy-se_entropy, fill=test_part),alpha=0.5) +
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725", "black")) +
    scale_color_manual(values=c("#69b3a2", "#404080", "black", "black")) +
    labs(x='click number', y='') +
    theme_classic() +
    scale_x_continuous(breaks=seq(20))+
  theme(legend.pos='na')

ggsave('figures/Hangman2/sequential_guess_entropy.png',width=2.5,height=1.5,dpi=300)
